TBD

### 2021-03-16 outputs/paper/paper.Rmd
S8 regressions + table complete (also S9),
Need to fine tweak the S9 regression by making a money and big money dummy variable + ensure the tables parse correctly when type = latex when the pdf knitted. S9 is currently having issues.

---
title: "TBD"
subtitle: "TBD"
author: "Bongju Yoo and Najma Osman"
thanks: "Code and data are available at: https://github.com/bonjwow/lost-wallet"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)

library(olsrr)
library(plm)

@@

```{r S8, echo = FALSE, message = FALSE}

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept

# conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

s8 <- dfBehavModel %>%
  filter(cond == 0 | cond == 1)

### money vs no money

# proportional test

# regression (for whatever reason, can't do fixed effects for city + institution using plm without issues)

s8_main_result <- lm(response ~ cond, data = s8)
summary(s8_main_result)

# regression by country

s8_by_country <- lm(response ~ cond + male + above40 + coworkers + computer + other_bystanders, data = s8)
summary(s8_by_country)

# final table (S8)

@@

```{r S9, echo = FALSE, message = FALSE}

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Bongju Yoo and Najma Osman"
thanks: "Code and data are available at: https://github.com/bonjwow/lost-wallet"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
header-includes:
   - \usepackage{dcolumn} 
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
library(stargazer)

@@

```{r S8, echo = FALSE, message = FALSE, warning = FALSE, results = 'asis'}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

# code dummy variables
s8_model <- dfBehavModel
s8_model$cond <- ifelse(s8_model$cond < 1, 0, 1)

# regression models
s8_main_result <- lm(response ~ cond, data = s8_model)
s8_money_result <- lm(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_model)

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"),
          column.labels = c("No Money", "Money"))

@@

```{r S9, echo = FALSE, warning = FALSE, message = FALSE}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

# controls:
  # fixed effects for institution and city
  # treatment condition
# binary controls:
  # situation
  # recipient
  # other treatments

### conditions (money vs big money) - next step is creating dummy variables for big money + money to finalize the table

# UK, Poland, and US
s9_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40)
s9_main_result <- lm(response ~ cond, data = s9_main)

# UK
s9_uk <- s9_main %>%
  filter(country == 39)
s9_uk_result <- lm(response ~ cond, data = s9_uk)

# Poland
s9_poland <- s9_main %>%
  filter(country == 27)

s9_poland_result <- lm(response ~ cond, data = s9_poland)

# USA
s9_usa <- s9_main %>%
  filter(country == 40)
s9_usa_result <- lm(response ~ cond, data = s9_usa)

# final table
stargazer(s9_main_result, s9_uk_result, s9_poland_result, s9_usa_result, 
          title = "Reporting rates in NoMoney, Money, and Big Money condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```
